Crop adaptation through gene flow

### 2016-07-01 crop_adaptation_gene_flow_gj_outline.tex
Update crop_adaptation_gene_flow_gj_outline.tex

Since the work of Charles Rick in 1940s and 50s \cite{rick1953novel}\, breeding efforts have focused on incorporating and utilizing the relatively diverse genetic germplasm of wild tomato relatives \cite{rick1988tomato, miller1990rflp, rick1982potential}\.
Wild tomato relatives have been shown to harbor resistance genes for more than 40 agronomically important diseases, and breeders are working to introgress them into cultivated tomato \cite{rick1995utilization}\.
Also, \cite{hanson2000mapping} mapped a tomato yellow leaf curl virus resistance gene in an accession of \emph{L. hirsutum f. glabratum} \cite{banerjee1990transfer} to an introgression on chromosome 11, which originated from the wild relative \emph{L. hirsutum}.
Similar resistance traits has also been shown to have been imparted from \emph{L. chilense}, \emph{L. pimpinellifolium}, and \emph{L. cheesmanii} \cite{hanson2000mapping}.

@@

>>>>

And yet, \cite{bai2007domestication} claim that "[m]ost likely, no exhange of genetic information with the wild germplasm took place until 1940."
It seems more likely that such genetic exchange would simply have been unintentional, rather than strictly nonexistent.
Since the work of Charles Rick in 1940s and 50s \cite{rick1953novel}\, breeding efforts have focused on incorporating and utilizing the relatively diverse genetic germplasm of wild tomato relatives \cite{rick1988tomato, miller1990rflp, rick1982potential}\.
Wild tomato relatives have been shown to harbor resistance genes for more than 40 agronomically important diseases, and breeders are working to introgress them into cultivated tomato \cite{rick1995utilization}\.
\cite{rick1958role} summarizes morphological evidence of natural introgressive hybridization with wild relatives in South America, despite cultivated tomato's proclivity to self-pollinate.
Also, \cite{hanson2000mapping} mapped a tomato yellow leaf curl virus resistance gene in an accession of \emph{L. hirsutum f. glabratum} \cite{banerjee1990transfer} to an introgression on chromosome 11, which originated from the wild relative \emph{L. hirsutum}.
Similar resistance traits has also been shown to have been imparted from \emph{L. chilense}, \emph{L. pimpinellifolium}, and \emph{L. cheesmanii} \cite{hanson2000mapping}.

@@

From disentangling:
domesticate/wild hybridization is still possible, but with diminished vigor [[50,55]]
Gene flow would be diminished during cultivation

http://link.springer.com/chapter/10.1007/978-0-387-92765-7_3
